---
title: "Visualizing One Numeric Variable"
output: github_document
---

We are requested to answer these questions:

    1. What is the average movie runtime?
    2. Are there any outliers?
    3. How spread out are the movie runtimes?
    4. What is the shape of the runtime distribution?
    
    
Univariate visualizations of a quantitiative variable


## Setup environment

```{r}
library(ggplot2)
movies = read.csv("../data/Movies.csv")
main_title <- "Distribution of Movies Runtimes"
x_lab = "Runtime in minutes"
```

## Plot

Create dot plot
```{r}
ggplot(
  data = movies,
  aes(x=Runtime, stat= "Count")) +
  geom_dotplot(binwidth = 1) +
  ggtitle(main_title) + 
  xlab(x_lab)
```

Create a Violin-Style dot plot
```{r}
ggplot(
  data = movies,
  aes(x = Runtime, stat = "count")) +
  geom_dotplot(
    binwidth = 1,
    stackdir = "center") +
  ggtitle(main_title) +
  xlab(x_lab)
```

## Boxplot

Create box plot of runtime
```{r}
ggplot(
  data = movies,
  aes(x= Runtime, y=Runtime)) +
  geom_boxplot() + 
  coord_flip() +
  ggtitle(main_title) + 
  xlab("") +
  ylab(x_lab) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())
```

## Histogram

Create histogram with ggplot

```{r}
ggplot(
data = movies,
aes(x = Runtime)) +
geom_histogram(binwidth = 10) +
  ggtitle(main_title) + 
  xlab(x_lab)
```

## Density plot

Create density plot with ggplot

```{r}
ggplot(
  data = movies,
  aes(x=Runtime)) +
  geom_density() +
  ggtitle(main_title) +
  xlab(x_lab)
```

## All in one

