---
title: "Visualizing Two Numeric Variables"
output: github_document
---

We are requested to answer these questions:

    1. How are runtime and box-office revenue related?
    2. Has the average box-office revenue changed over time?
    
    
*Bivariate Visualization for two quantitiative variables*
## Setting up environment

```{r}
library(lattice)
movies <- read.csv('../data/Movies.csv')
main_label <- "Runtime vs. Box Office Revenue"
runtime_in_minutes_label <- "Runtime (minutes)"
box_office_label <- "Box Office ($M)"
density_label <- "Density"
```

## Plots


### Scatter Plot
Create a scatterplot

```{r}
xyplot(
  x = Box.Office ~ Runtime,
  data = movies,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

#### Adding a regression line

```{r}
xyplot(
  x = Box.Office ~ Runtime,
  data = movies,
  type = c("p","r"), # p stands for points and r stands for regression
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

### Load hexbin library
```{r}
library(hexbin)
```

### Hexagonal binned frequency heatmap

Create hexagonal binned frequency heatmap

```{r}
hexbinplot(
  x = Box.Office ~ Runtime,
  data = movies,
  xbins = 30,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

### Grid from our 2D kernel density estimate

Create a grid from our 2D kernel density estimate, the data structure is a *data frame*

```{r}
grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

```

Display the data frame

```{r}
head(grid)
```

### Contour plot of density

Create a contour plot of density

```{r}
contourplot(
  x = z ~ x* y,
  data = grid,
  main = main_label,
  xlab = 
)
```



