---
title: "Data Visualization - Quantitative Univariate Analysis"
output: github_document
---

# Data Load

Let's start by taking a look to our current dataset


```{r}
library(tidyverse)
library(ggplot2)
library(dslabs)
library(forcats)

load("rda/apps_dataset.rda")
load("rda/apps_categories_dataset.rda")
load("rda/apps_genres_dataset.rda")
load("rda/apps_versions_dataset.rda")
ds_theme_set()
```

# Data Visualization

So now our data is loaded, let's start by making questions that may fit on the course structure.

## Quantitative Univariate Analysis

**Questions to answer**
    
    * What is the app rating mean/max/min?
    * What is the app reviews mean/max/min?
    * What is the app size mean/max/min?
    * What is the app average price for an app?
    * What is the app installation distribution?
    * Are apps popularity in 2018 still high in comprarisson to previous years?
    

### What is the app rating mean/max/min?

Setting up initial variables
```{r}
title <- "Distribution of App Ratings"
x_lab <- "Ratings"
y_lab <- "Count"
```


#### Dot Plot
As pointed out in this [link](https://ggplot2.tidyverse.org/reference/geom_dotplot.html) :  

*When binning along the x axis and stacking along the y axis, the numbers on y axis are not meaningful, due to technical limitations of ggplot2. You can hide the y axis, as in one of the examples, or manually scale it to match the number of dots.*  

So we also specify the y axis scale and the dot size, so we can display an approximation to the real distribution.


```{r}

apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, stat = "Count")) +
  geom_dotplot(binwidth = .1, dotsize = .018) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_y_continuous(limits = c(-1, 1200))

```


####Violin dot plot

```{r}

apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, stat="count")) +
  geom_dotplot(
    binwidth = .1,
    dotsize = 0.02,
    stackdir = "center") +
  ggtitle(title) +
  xlab(x_lab)
  
```


#### Boxplot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y=Rating)) +
  geom_boxplot() +
  ggtitle(title) +
  xlab("") + 
  ylab(x_lab) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())
```


#### Histogram

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating)) +
  geom_histogram(binwidth = .1) +
  ggtitle(title) +
  xlab(x_lab) + 
  ylab(y_lab)
```


#### Density Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x=Rating)) +
  geom_density() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```



#### Answer
*Question: What is the app rating mean/max/min?*


### What is the app reviews mean/max/min?

#### Answer
*Question: What is the app reviews mean/max/min?*

### What is the app size mean/max/min?

#### Answer
*Question: What is the app size mean/max/min?*

### What is the app average price for an app?

#### Answer
*Question: What is the app average price for an app?*

### What is the app installation distribution?

#### Answer
*Question: What is the app installation distribution?*


### Are apps popularity in 2018 still high in comprarisson to previous years?

#### Answer
*Question: Are apps popularity in 2018 still high in comprarisson to previous years?*