---
title: "Data Visualization - Quantitative Univariate Analysis"
output: github_document
---

# Data Load

Let's start by taking a look to our current dataset


```{r}
library(tidyverse)
library(ggplot2)
library(dslabs)
library(forcats)
library(lattice)
load("rda/apps_dataset.rda")
load("rda/apps_categories_dataset.rda")
load("rda/apps_genres_dataset.rda")
load("rda/apps_versions_dataset.rda")
ds_theme_set()
```

# Data Visualization

So now our data is loaded, let's start by making questions that may fit on the course structure.

## Quantitative Univariate Analysis

**Questions to answer**
    
    * What is the app rating mean/max/min?
    * What is the app reviews mean/max/min?
    * What is the app size mean/max/min?
    * What is the app average price for an app?
    * What is the app installation distribution?
    * Are apps popularity in 2018 still high in comprarisson to previous years?
    

### What is the app rating mean/max/min?

Setting up initial variables
```{r}
title <- "Distribution of App Ratings"
x_lab <- "Ratings"
y_lab <- "Count"
```


#### Dot Plot
As pointed out in this [link](https://ggplot2.tidyverse.org/reference/geom_dotplot.html) :  

*When binning along the x axis and stacking along the y axis, the numbers on y axis are not meaningful, due to technical limitations of ggplot2. You can hide the y axis, as in one of the examples, or manually scale it to match the number of dots.*  

So we also specify the y axis scale and the dot size, so we can display an approximation to the real distribution.


```{r}

apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, stat = "Count")) +
  geom_dotplot(binwidth = .1, dotsize = .018) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_y_continuous(limits = c(-1, 1200))

```

So we create it using Lattice


```{r}
apps_versions_dataset %>%
 stripplot(x= ~ Rating,
           main = title,
           xlab = x_lab) 

```


#### Dot Plot Jitter


```{r}
apps_versions_dataset %>%
  stripplot( x= ~Rating,
             main = title,
             xlab = x_lab,
             jitter = TRUE,
             amount = 3)
```



#### Violin dot plot

```{r}

apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, stat="count")) +
  geom_dotplot(
    binwidth = .1,
    dotsize = 0.02,
    stackdir = "center") +
  ggtitle(title) +
  xlab(x_lab)
  
```


#### Boxplot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y=Rating)) +
  geom_boxplot() +
  ggtitle(title) +
  xlab("") + 
  ylab(x_lab) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())
```


#### Histogram

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating)) +
  geom_histogram(binwidth = .1) +
  ggtitle(title) +
  xlab(x_lab) + 
  ylab(y_lab)
```


#### Density Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x=Rating)) +
  geom_density() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```



#### Answer



### What is the app reviews mean/max/min?

#### Dot Plot

```{r}
title <- "Distribution of Reviews"
x_lab <- "Ratings"

apps_versions_dataset %>%
  ggplot(aes( x= Reviews, stat="count")) +
  geom_dotplot(binwidth = 10) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)

```


```{r}
apps_versions_dataset %>%
  stripplot(
    x = ~ Reviews,
    main = title,
    xlab = x_lab)

```


#### Dot Plot Jitter

```{r}
apps_versions_dataset %>%
  stripplot( 
    x = ~Reviews,
    main = title,
    xlab = x_lab,
    jitter = TRUE,
    amount = 1)
```


#### Violin Plot

```{r}
apps_versions_dataset %>%
  ggplot(aes(x=Reviews, stat = "count")) +
  geom_dotplot(binwidth = 10, stackdir = "center") +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)

```


#### Box Plot

```{r}
apps_versions_dataset %>%
  ggplot(aes(x = Reviews, y = Reviews)) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab("") +
  geom_boxplot() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())
  
```


#### Histogram

```{r}
apps_versions_dataset %>%
  ggplot(aes(x = Reviews)) +
  geom_histogram(binwidth = 200) +
  ggtitle(title) +
  xlab(x_lab) + 
  ylab(y_lab)
  
```



#### Density

```{r}
apps_versions_dataset %>%
  ggplot(aes(x = Reviews)) +
  geom_density() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```




#### Answer



### What is the app size mean/max/min?

#### Dot Plot

```{r}
title <- "Distribution of App Size"
x_lab <- "App Size"

apps_versions_dataset %>%
  ggplot(aes(x = SizeNumeric, stat = "count")) +
  geom_dotplot(binwidth = .2) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
  
```


```{r}
apps_versions_dataset %>%
  stripplot(x = ~ SizeNumeric,
            main= title,
            xlab = x_lab) 
```



#### Dot Plot Jitter

```{r}
apps_versions_dataset %>%
  stripplot(x = ~SizeNumeric,
            main =title,
            xlab = x_lab,
            jitter = TRUE, 
            amount = 2)
```


#### Violin Plot

```{r}
apps_versions_dataset  %>% 
  ggplot(aes(x = SizeNumeric, stat = "count"))  +
  geom_dotplot(binwidth = .2, stackdir = "center") +
  ggtitle(title) + 
  xlab(x_lab) +
  ylab(y_lab)

```


#### Box Plot

```{r}
apps_versions_dataset %>%
  ggplot(aes(x = SizeNumeric, y = SizeNumeric)) +
  geom_boxplot() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab("")
```



#### Histogram

```{r}
apps_versions_dataset %>%
  ggplot(aes(x=SizeNumeric)) +
  geom_histogram(binwidth = 2) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```



#### Density
```{r}
apps_versions_dataset %>%
  ggplot(aes(x = SizeNumeric)) +
  geom_density() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
  
```



#### Answer
*Question: What is the app size mean/max/min?*

### What is the app average price for an app?

#### Dot Plot


#### Dot Plot Jitter


#### Violin Plot


#### Box Plot


#### Histogram


#### Density

#### Answer
*Question: What is the app average price for an app?*

### What is the app installation distribution?

#### Dot Plot


#### Dot Plot Jitter


#### Violin Plot


#### Box Plot


#### Histogram


#### Density

#### Answer
*Question: What is the app installation distribution?*


### Are apps popularity in 2018 still high in comprarisson to previous years?

#### Dot Plot


#### Dot Plot Jitter


#### Violin Plot


#### Box Plot


#### Histogram


#### Density

#### Answer
*Question: Are apps popularity in 2018 still high in comprarisson to previous years?*