---
title: "Data Visualization"
output: github_document
---

# Data Load

Let's start by taking a look to our current dataset


```{r}
library(tidyverse)
library(ggplot2)
library(dslabs)
library(forcats)

load("rda/apps_dataset.rda")
ds_theme_set()
head(apps_dataset)
```

# Data Visualization

So now our data is loaded, let's start by making questions that may fit on the course structure.

## Qualitative Univariate Analysis

**Questions to answer**


    * How many apps are in each app category?
    * How many apps are in each installation range?
    * What proportion of apps are paid apps?
    * How many apps are in each app content rating?
    * How many apps are in each app genre?
    * What proportion of apps are supporting the latest version?
    
### How many apps are in each app category?

#### Frequency chart

```{r}

apps_dataset %>% 
  ggplot(aes(x =fct_infreq(Category))) +
  geom_bar() +
  ggtitle("Count of Apps by Category") +
  xlab("Category") +
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 90))

```


```{r}

apps_dataset %>% 
  ggplot(aes(x =fct_rev(fct_infreq(Category)))) +
  coord_flip() +
  geom_bar() +
  ggtitle("Count of Apps by Category") + 
  xlab("Count") +
  ylab("Category") +
  theme(axis.text.x = element_text(angle = 90))
```


    
## Quantitative Univariate Analysis

**Questions to answer**
    
    * What is the app rating mean/max/min?
    * What is the app reviews mean/max/min?
    * What is the app size mean/max/min?
    * What is the app average price for an app?
    * What is the app installation distribution?
    * Are apps popularity in 2018 still high in comprarisson to previous years?
    

## Qualitative Bivariate Analysis

**Questions to answer**



## Quantitative Bivariate Analysis

**Questions to answer**


## Qualitative and Quantitative Bivariate Analysis

**Questions to answer**
    
    
    
    
    